\chameleon{}: Untangling Type Errors Through Interactive Visualization and Exploration

### 2023-03-10 sections/introduction.tex
Latest

Our experiments showed that programmers using \chameleon{} fix type errors faster than with traditional text-based error messages. This difference is more significant when solving harder tasks. Further, programmers who actively use \chameleon{} interactive features fix type errors faster than simply reading the type error output. Although \chameleon{} is designed to work with
the Haskell language, we plan to extend the underlying ideas to work with other strongly typed languages.

>>>>

Our experiments showed that programmers using \chameleon{} fix type errors faster than with traditional text-based error messages. This difference is more significant when solving harder tasks. Further, programmers who actively use \chameleon{} interactive features fix type errors faster than simply reading the type error output. Although \chameleon{} is designed to work with
the Haskell language, we plan to extend the underlying ideas to work with other strongly typed languages, such as Rust or TypeScript..
